Cluster Analysis

### 2020-07-31 MSDS 411 assign 4.Rmd
test
knit the code into an html file

---
title: 'Cluster Analysis'
author: "Nadia Noui-Mehidi"
date: "11/5/2019"
output: rmarkdown::github_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

>>>>

---
title: "Cluster Analysis"
author: "Nadia Noui-Mehidi"
output:
  github_document: default
  rmarkdown::github_documen: default
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
